### 2020-06-01 paper.tex
Add Second Subscection of Simulated Annealing
Add Third Subsection in Simulated Annealing Section

At this step, the total wirelength of cells interconnections will most likely be large due to them being placed randomly. Hence the presence of the rest of the subsequent procedures which aim to achieve the optimal placement of the cells.

\subsubsection{Move Generation Function}
\subsubsection{Cost Function}
\subsubsection{Annealing Schedule}

>>>>

At this step, the total wirelength of cells interconnections will most likely be large due to them being placed randomly. Hence the presence of the rest of the subsequent procedures which aim to achieve the optimal placement of the cells.
\medskip

\subsubsection{Move Generation Function}

At each iteration, cells are rearranged to generate a new placement configuration of the cells. To do so, there are two possible strategies used:
\begin{itemize}
    \item Move cells randomly to new legal positions 
    \item Swap the positions of each two cells
\end{itemize}
\medskip

\subsubsection{Cost Function}

The cost function consists of two terms as follows:
\begin{equation}
    C = C_{1} + C_{2}
\end{equation}
Where $C_{1}$ is the measure of the total wirelength and $C_{2}$ is the measure of total overlap of the chip which is sometimes neglected as in our case but it is used in other papers \cite{b16} nevertheless.

Let $d_{h}^{ij}$ $d_{v}^{ij}$ be the horizontal and the vertical distance between cell $i$ and its $j^{th}$ out cell respectively, the total wire length of the chip can be expressed as the following equation 
\begin{equation}
    C_{1} = \sum_{i=cell}^{n} \sum_{j=out cell}^{n} (d_{h}^{ij} + d_{v}^{ij})
\end{equation}
Where $n$ is the total number of cells in the chip 
In case of the second term $C_{2}$, whenever two cells are swapped, they might overlap, therefore, $O_{ij}$ indicates the overlap between cell $i$ and cell $j$, this overlap is undesirable and it negatively affects the cost function by increasing its value by the term $C_{2}$ which is the summation of each overlap value squared.
\begin{equation}
    C_{2} = \sum_{i!=j} (O_{ij}^{2})
\end{equation}
The cost function is calculated at each iteration after generating a new cells layout.
\medskip

\subsubsection{Annealing Schedule}
